State of the Art in Concurrent Priority Queues \\ Student Paper for Seminar in Algorithms 2013W \\ Technical University of Vienna

### 2014-03-20 paper/paper.tex
DeleteMin removes lowest priority item

This paper focuses on the priority queue data structure, consisting of two operations
traditionally called \lstinline|Insert| and \lstinline|DeleteMin|. \lstinline|Insert|
places an item into the queue together with its priority, while \lstinline|DeleteMin|
removes and returns the highest priority item. Both of these operations are expected to have
a complexity of at most $O(\log n)$. Priority queues are used in a large variety
of situations such as shortest path algorithms and scheduling. % See liu2012lock for more.

@@

Priority queues are an abstract data structure allowing insertion of items with a given priority
and removal of the highest-priority item in logarithmic time. Search trees and Heaps (which are 
flattened representations of complete trees such that each node's value is at least as large as
those of both children) are concrete data structures which are usually used to implement sequential
priority queues. However, both require fairly elaborate reorganization after \lstinline|DeleteMin|
and/or \lstinline|Insert| operations, which are especially challenging to achieve in a concurrent
environment.

>>>>

This paper focuses on the priority queue data structure, consisting of two operations
traditionally called \lstinline|Insert| and \lstinline|DeleteMin|. \lstinline|Insert|
places an item into the queue together with its priority, while \lstinline|DeleteMin|
removes and returns the lowest priority item. Both of these operations are expected to have
a complexity of at most $O(\log n)$. Priority queues are used in a large variety
of situations such as shortest path algorithms and scheduling. % See liu2012lock for more.

@@

Priority queues are an abstract data structure allowing insertion of items with a given priority
and removal of the lowest-priority item in logarithmic time. Search trees and Heaps (which are
flattened representations of complete trees such that each node's value is at least as large as
those of both children) are concrete data structures which are usually used to implement sequential
priority queues. However, both require fairly elaborate reorganization after \lstinline|DeleteMin|
and/or \lstinline|Insert| operations, which are especially challenging to achieve in a concurrent
environment.
